A multi-scale story of the diffusion of a new technology: the web

### 2024-06-12 presentations/web_diffusion.Rmd
presentation

```{r , eval=T, fig.height=5, fig.width=5, message=FALSE}
path.image <- paste0(path, "/outputs/ranks/web_per_firm2000_2012_only05.png")
knitr::include_graphics(path.image)
```

@@

```{r , eval=T, fig.height=5, fig.width=5, message=FALSE}
path.image <- paste0(path, "/outputs/ranks/web_per_firm2000_2012_only95.png")
knitr::include_graphics(path.image)
```

@@

```{r lisa_la, results='asis', out.width = "30%"}
path.images <- paste0(path, "/outputs/la_ggplot/lisa/")

@@

```{r lisa_oa, eval=T,results='asis', out.width = "30%"}
path.images <- paste0(path, "/outputs/oa_ggplot/lisa/")

>>>>

```{r , eval=T, fig.height=5, fig.width=5, message=FALSE}
path.image <- paste0(path, "/outputs/ranks/web_per_firm2000_2012_only05_av.png")
knitr::include_graphics(path.image)
```

@@

```{r , eval=T, fig.height=5, fig.width=5, message=FALSE}
path.image <- paste0(path, "/outputs/ranks/web_per_firm2000_2012_only95_av.png")
knitr::include_graphics(path.image)
```

@@

```{r lisa_la, results='asis', out.width = "60%"}
path.images <- paste0(path, "/outputs/lisa/la_ggplot/")

@@

```{r lisa_oa, eval=T,results='asis', out.width = "60%"}
path.images <- paste0(path, "/outputs/lisa/oa_ggplot/")
